\texttt{MSnbase}, efficient R-based access and manipulation of raw mass spectrometry data

### 2019-06-05 msnbase2.Rnw
intro to main section

@@

- visualisation
- large scale data analyses (metabolomics, Johannes)
- boxcar prototyping

>>>>

We are going to present the new raw data infrastructure that has been
available since \texttt{MSnbase} version 2.0, and then describe how it
is leveraged to process large amount of data. We are then going to
demonstrate some visualisation that make use of the raw data
structures available in \texttt{MSnbase} and conlude with an example
if flexible prototyping, by showing how to quickly combine spectra
acquired using the Boxcar method (REF).

@@

- large scale data analyses (metabolomics, Johannes)

- visualisation: Jo's XIC plots, possibly also MSMap, with animation.

- boxcar prototyping
